---
title: "clusterBMA_reviewer_additions"
author: "Owen Forbes"
date: "06/01/2023"
output: html_document
---



```{r setup, include=FALSE}
library(clusterBMA) #v0.2.0
library(diceR) #v1.2.2 for consensus clustering - CSPA, majority voting, etc

library(tidyverse) #v1.3.2 for data cleaning/piping etc


library(clusterGeneration)#v1.3.7 for simulated data


library(pdfCluster) #v1.0-4 for adjusted Rand index

```



# IMPLEMENTING FOR COMPARISON OF clusterBMA and diceR ensemble methods...

1. use consensus_cluster() to calculate variety of clustering results (9 algs), using p.item =1 to not do subsampling

2. calculate consensus using diff methods: LCA(), LCE(), majority_voting(), k_modes(), CSPA()

3. apply clusterBMA

4. compare
- % correctly recovered labels (accuracy results)
--> ADJUSTED RAND INDEX
- accuracy results for cBMA allocations with uncertainty <30%? (or some other threshold)
- additional information gained


# ALGORITHM OUTPUTS (hard or soft?) from diceR


# 9 ALGORITHMS

# looking under the hood at algos


#HC = hard

as.integer(stats::cutree(stats::hclust(d, method = method), 
        k))
        
#DIANA = hard
 as.integer(stats::cutree(cluster::diana(d, diss = TRUE), 
            k))

#PAM = hard
as.integer(cluster::pam(d, k, cluster.only = TRUE))

#k-means = hard
as.integer(stats::kmeans(x, k)$cluster)

#ap Affinity Propagation = has probabilistic interpretation available, but for all intents and purposes it's hard allocation... 
#see http://genes.toronto.edu/affinitypropagation/faq.html
# Is there a probabilistic interpretation of affinity propagation?

suppressWarnings(apcluster::apclusterK(apcluster::negDistMat, 
            x, k, verbose = FALSE)@idx) %>% dplyr::dense_rank() %>% 
            purrr::when(length(.) > 0 ~ ., ~NA)


# sc Spectral clustering = hard
kernlab::specc(as.matrix(x), k, kernel = "rbfdot")@.Data

        

#GMM = soft

# If wanting to use within-method uncertainty/probabilistic cluster allocation, need to generate gmm from mclust::Mclust
mclust::Mclust(x, k, verbose = FALSE)$classification


--------


# SIMULATION STUDY 1


```{r}



simul_data_2d <- clusterGeneration::genRandomClust(numClust=3,sepVal=-0.2,numNonNoisy=2,numNoisy=0,clustSizes=c(rep(200,3)),numReplicate = 1,clustszind = 3)
simul_2d_df <- simul_data_2d$datList$test_1
simul_2d_labels <- simul_data_2d$memList$test_1

simul_data_10d <- clusterGeneration::genRandomClust(numClust=3,sepVal=-0.2,numNonNoisy=10,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 1,clustszind = 3)
simul_10d_df <- simul_data_10d$datList$test_1
simul_10d_labels <- simul_data_10d$memList$test_1


simul_data_50d <- clusterGeneration::genRandomClust(numClust=3,sepVal=-0.2,numNonNoisy=50,numNoisy=0,clustSizes=c(rep(200,3)),numReplicate = 1,clustszind = 3)
simul_50d_df <- simul_data_50d$datList$test_1
simul_50d_labels <- simul_data_50d$memList$test_1

# 
# sim_data_1_10_50_190123 <- list(simul_data_2d,simul_data_10d,simul_data_50d)
# save(sim_data_1_10_50_190123,file="sim_data_1_10_50_190123")

load("sim_data_1_10_50_190123")

simul_data_2d <- sim_data_1_10_50_190123[[1]]
simul_data_10d <- sim_data_1_10_50_190123[[2]]
simul_data_50d <- sim_data_1_10_50_190123[[3]]

simul_2d_df <- simul_data_2d$datList$test_1
simul_2d_labels <- simul_data_2d$memList$test_1

simul_10d_df <- simul_data_10d$datList$test_1
simul_10d_labels <- simul_data_10d$memList$test_1

simul_50d_df <- simul_data_50d$datList$test_1
simul_50d_labels <- simul_data_50d$memList$test_1

 
plot(simul_2d_df)


```


#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
# 2 dimensional sim


```{r}



diceR_clusters_2d <- diceR::consensus_cluster(data=simul_2d_df,nk=3,p.item=1, algorithms = c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans"), reps = 1) #having issues with nmf and block - chucking

CSPA_output_2d <- CSPA(diceR_clusters_2d,k=3)

LCA_output_2d <- LCA(diceR_clusters_2d, is.relabelled = F)

LCE_output_2d <- LCE(as.matrix(diceR_clusters_2d[,1,,1]), k=3, sim.mat="cts")


k_modes_output_2d <- k_modes(diceR_clusters_2d, is.relabelled = F)

majority_voting_output_2d <- majority_voting(diceR_clusters_2d, is.relabelled = F)

```


# ALGORITHM OUTPUTS (hard or soft?) from diceR




```{r}
#algorithms = c("hc", "diana", "km", "pam", "ap", "sc","gmm", "som", "cmeans")

# CHUCKED NMF AND BLOCK which were having issues with weights (XB) and NAs
#nmf_brunet_probs <- hard_to_prob_fn(cluster_labs_diceR[,1],n_clust=3)
#nmf_lee_probs <- hard_to_prob_fn(cluster_labs_diceR[,2],n_clust=3)
#block_probs <- hard_to_prob_fn(cluster_labs_diceR[,10],n_clust=3)



cluster_labs_diceR_2d <- as.matrix(diceR_clusters_2d[,1,,1])

hc_probs_2d <- hard_to_prob_fn(cluster_labs_diceR_2d[,1],n_clust=3)
diana_probs_2d <- hard_to_prob_fn(cluster_labs_diceR_2d[,2],n_clust=3)
km_probs_2d <- hard_to_prob_fn(cluster_labs_diceR_2d[,3],n_clust=3)
pam_probs_2d <- hard_to_prob_fn(cluster_labs_diceR_2d[,4],n_clust=3)
ap_probs_2d <- hard_to_prob_fn(cluster_labs_diceR_2d[,5],n_clust=3)
sc_probs_2d <- hard_to_prob_fn(cluster_labs_diceR_2d[,6],n_clust=3)
gmm_probs_2d <- hard_to_prob_fn(cluster_labs_diceR_2d[,7],n_clust=3)
som_probs_2d <- hard_to_prob_fn(cluster_labs_diceR_2d[,8],n_clust=3)
cmeans_probs_2d <- hard_to_prob_fn(cluster_labs_diceR_2d[,9],n_clust=3)


list_of_probs_2d <- list(hc_probs_2d,diana_probs_2d,km_probs_2d,pam_probs_2d,ap_probs_2d,sc_probs_2d,gmm_probs_2d,som_probs_2d,cmeans_probs_2d)

cBMA_output_2d <- clusterBMA::clusterBMA(input_data = simul_2d_df,cluster_prob_matrices = list_of_probs_2d,n_final_clust = 3,wt_crit_name = "Calinski_Harabasz",wt_crit_direction = "max")
cBMA_output_2d
#cBMA_output_2d_sdbw <- clusterBMA::clusterBMA(input_data = simul_2d_df,cluster_prob_matrices = list_of_probs_2d,n_final_clust = 3,wt_crit_name = "S_Dbw",wt_crit_direction = "min")



cBMA_output_2d[[3]]
cBMA_output_2d[[5]]

#cBMA_output_2d_sdbw[[5]]
#cBMA_output_2d[[5]]
```


# Combining outputs all into one DF

```{r}

true_labs_2d <- simul_2d_labels

plotting_df_2d <- data.frame(cbind(simul_2d_df,CSPA_output_2d,LCA_output_2d,LCE_output_2d,k_modes_output_2d,majority_voting_output_2d,cBMA_output_2d[[3]]$alloc_ordered,cBMA_output_2d[[3]]$alloc_prob,true_labs_2d))
# 
# names(plotting_df)
# length(plotting_df)
# plotting_df[,4:8] <- lapply(plotting_df[,4:8],as.factor)

names(plotting_df_2d)[ncol(plotting_df_2d)-2] <- "clusterBMA_output_2d" 
names(plotting_df_2d)[ncol(plotting_df_2d)-1] <- "clusterBMA_probs_2d" 

#view(plotting_df)
```


# comparing accuracy using Adjusted RAnd Index

```{r}
library(pdfCluster)

names(plotting_df_2d)


# CSPA
ARI_CSPA_2d <- pdfCluster::adj.rand.index(plotting_df_2d$CSPA_output_2d,plotting_df_2d$true_labs_2d)


# LCA
ARI_LCA_2d <- pdfCluster::adj.rand.index(plotting_df_2d$LCA_output_2d,plotting_df_2d$true_labs_2d)

# LCE
ARI_LCE_2d <- pdfCluster::adj.rand.index(plotting_df_2d$LCE_output_2d,plotting_df_2d$true_labs_2d)


# k_modes
ARI_k_modes_2d <- pdfCluster::adj.rand.index(plotting_df_2d$k_modes_output_2d,plotting_df_2d$true_labs_2d)


# majority_voting
ARI_majority_voting_2d <- pdfCluster::adj.rand.index(plotting_df_2d$majority_voting_output_2d,plotting_df_2d$true_labs_2d)


# clusterBMA
ARI_clusterBMA_2d <- pdfCluster::adj.rand.index(plotting_df_2d$clusterBMA_output_2d,plotting_df_2d$true_labs_2d)


highcertainty_threshold <- 0.8
ARI_clusterBMA_highcertainty_2d <- pdfCluster::adj.rand.index(plotting_df_2d$clusterBMA_output_2d[cBMA_output_2d[[3]]$alloc_prob>highcertainty_threshold],plotting_df_2d$true_labs_2d[cBMA_output_2d[[3]]$alloc_prob>highcertainty_threshold])

ARI_CSPA_2d
ARI_LCA_2d
ARI_LCE_2d
ARI_k_modes_2d
ARI_majority_voting_2d
ARI_clusterBMA_2d
ARI_clusterBMA_highcertainty_2d


# how many high-certainty (>90% alloc prob) allocations?

sum(cBMA_output_2d[[3]]$alloc_prob>highcertainty_threshold) #569/600





```














#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
# 10 dimensional sim


```{r}



diceR_clusters_10d <- diceR::consensus_cluster(data=simul_10d_df,nk=3,p.item=1, algorithms = c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans"), reps = 1) #having issues with nmf and block - chucking

CSPA_output_10d <- CSPA(diceR_clusters_10d,k=3)

LCA_output_10d <- LCA(diceR_clusters_10d, is.relabelled = F)

LCE_output_10d <- LCE(as.matrix(diceR_clusters_10d[,1,,1]), k=3, sim.mat="cts")


k_modes_output_10d <- k_modes(diceR_clusters_10d, is.relabelled = F)

majority_voting_output_10d <- majority_voting(diceR_clusters_10d, is.relabelled = F)

```


# ALGORITHM OUTPUTS (hard or soft?) from diceR




```{r}
#algorithms = c("hc", "diana", "km", "pam", "ap", "sc","gmm", "som", "cmeans")

# CHUCKED NMF AND BLOCK which were having issues with weights (XB) and NAs
#nmf_brunet_probs <- hard_to_prob_fn(cluster_labs_diceR[,1],n_clust=3)
#nmf_lee_probs <- hard_to_prob_fn(cluster_labs_diceR[,2],n_clust=3)
#block_probs <- hard_to_prob_fn(cluster_labs_diceR[,10],n_clust=3)



cluster_labs_diceR_10d <- as.matrix(diceR_clusters_10d[,1,,1])

hc_probs_10d <- hard_to_prob_fn(cluster_labs_diceR_10d[,1],n_clust=3)
diana_probs_10d <- hard_to_prob_fn(cluster_labs_diceR_10d[,2],n_clust=3)
km_probs_10d <- hard_to_prob_fn(cluster_labs_diceR_10d[,3],n_clust=3)
pam_probs_10d <- hard_to_prob_fn(cluster_labs_diceR_10d[,4],n_clust=3)
ap_probs_10d <- hard_to_prob_fn(cluster_labs_diceR_10d[,5],n_clust=3)
sc_probs_10d <- hard_to_prob_fn(cluster_labs_diceR_10d[,6],n_clust=3)
gmm_probs_10d <- hard_to_prob_fn(cluster_labs_diceR_10d[,7],n_clust=3)
som_probs_10d <- hard_to_prob_fn(cluster_labs_diceR_10d[,8],n_clust=3)
cmeans_probs_10d <- hard_to_prob_fn(cluster_labs_diceR_10d[,9],n_clust=3)


list_of_probs_10d <- list(hc_probs_10d,diana_probs_10d,km_probs_10d,pam_probs_10d,ap_probs_10d,sc_probs_10d,gmm_probs_10d,som_probs_10d,cmeans_probs_10d)

cBMA_output_10d <- clusterBMA::clusterBMA(input_data = simul_10d_df,cluster_prob_matrices = list_of_probs_10d,n_final_clust = 3,wt_crit_name = "Calinski_Harabasz",wt_crit_direction = "max")
cBMA_output_10d

cBMA_output_10d[[3]]
cBMA_output_10d[[5]]
```


# Combining outputs all into one DF

```{r}

true_labs_10d <- simul_10d_labels

plotting_df_10d <- data.frame(cbind(simul_10d_df,CSPA_output_10d,LCA_output_10d,LCE_output_10d,k_modes_output_10d,majority_voting_output_10d,cBMA_output_10d[[3]]$alloc_ordered,cBMA_output_10d[[3]]$alloc_prob,true_labs_10d))
# 
# names(plotting_df)
# length(plotting_df)
# plotting_df[,4:8] <- lapply(plotting_df[,4:8],as.factor)

names(plotting_df_10d)[ncol(plotting_df_10d)-2] <- "clusterBMA_output_10d" 
names(plotting_df_10d)[ncol(plotting_df_10d)-1] <- "clusterBMA_probs_10d" 

#view(plotting_df)
```


# comparing accuracy using Adjusted RAnd Index

```{r}
library(pdfCluster)

names(plotting_df_10d)


# CSPA
ARI_CSPA_10d <- pdfCluster::adj.rand.index(plotting_df_10d$CSPA_output_10d,plotting_df_10d$true_labs_10d)


# LCA
ARI_LCA_10d <- pdfCluster::adj.rand.index(plotting_df_10d$LCA_output_10d,plotting_df_10d$true_labs_10d)

# LCE
ARI_LCE_10d <- pdfCluster::adj.rand.index(plotting_df_10d$LCE_output_10d,plotting_df_10d$true_labs_10d)


# k_modes
ARI_k_modes_10d <- pdfCluster::adj.rand.index(plotting_df_10d$k_modes_output_10d,plotting_df_10d$true_labs_10d)


# majority_voting
ARI_majority_voting_10d <- pdfCluster::adj.rand.index(plotting_df_10d$majority_voting_output_10d,plotting_df_10d$true_labs_10d)


# clusterBMA
ARI_clusterBMA_10d <- pdfCluster::adj.rand.index(plotting_df_10d$clusterBMA_output_10d,plotting_df_10d$true_labs_10d)


highcertainty_threshold <- 0.8
ARI_clusterBMA_highcertainty_10d <- pdfCluster::adj.rand.index(plotting_df_10d$clusterBMA_output_10d[cBMA_output_10d[[3]]$alloc_prob>highcertainty_threshold],plotting_df_10d$true_labs_10d[cBMA_output_10d[[3]]$alloc_prob>highcertainty_threshold])

ARI_CSPA_10d
ARI_LCA_10d
ARI_LCE_10d
ARI_k_modes_10d
ARI_majority_voting_10d
ARI_clusterBMA_10d
ARI_clusterBMA_highcertainty_10d


# how many high-certainty (>90% alloc prob) allocations?

sum(cBMA_output_10d[[3]]$alloc_prob>highcertainty_threshold) #557/600



```











#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
# 50 dimensional sim


```{r}



diceR_clusters_50d <- diceR::consensus_cluster(data=simul_50d_df,nk=3,p.item=1, algorithms = c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans"), reps = 1) #having issues with nmf and block - chucking

CSPA_output_50d <- CSPA(diceR_clusters_50d,k=3)

LCA_output_50d <- LCA(diceR_clusters_50d, is.relabelled = F)

LCE_output_50d <- LCE(as.matrix(diceR_clusters_50d[,1,,1]), k=3, sim.mat="cts")


k_modes_output_50d <- k_modes(diceR_clusters_50d, is.relabelled = F)

majority_voting_output_50d <- majority_voting(diceR_clusters_50d, is.relabelled = F)

```


# ALGORITHM OUTPUTS (hard or soft?) from diceR




```{r}
#algorithms = c("hc", "diana", "km", "pam", "ap", "sc","gmm", "som", "cmeans")

# CHUCKED NMF AND BLOCK which were having issues with weights (XB) and NAs
#nmf_brunet_probs <- hard_to_prob_fn(cluster_labs_diceR[,1],n_clust=3)
#nmf_lee_probs <- hard_to_prob_fn(cluster_labs_diceR[,2],n_clust=3)
#block_probs <- hard_to_prob_fn(cluster_labs_diceR[,10],n_clust=3)



cluster_labs_diceR_50d <- as.matrix(diceR_clusters_50d[,1,,1])

hc_probs_50d <- hard_to_prob_fn(cluster_labs_diceR_50d[,1],n_clust=3)
diana_probs_50d <- hard_to_prob_fn(cluster_labs_diceR_50d[,2],n_clust=3)
km_probs_50d <- hard_to_prob_fn(cluster_labs_diceR_50d[,3],n_clust=3)
pam_probs_50d <- hard_to_prob_fn(cluster_labs_diceR_50d[,4],n_clust=3)
ap_probs_50d <- hard_to_prob_fn(cluster_labs_diceR_50d[,5],n_clust=3)
sc_probs_50d <- hard_to_prob_fn(cluster_labs_diceR_50d[,6],n_clust=3)
gmm_probs_50d <- hard_to_prob_fn(cluster_labs_diceR_50d[,7],n_clust=3)
som_probs_50d <- hard_to_prob_fn(cluster_labs_diceR_50d[,8],n_clust=3)
cmeans_probs_50d <- hard_to_prob_fn(cluster_labs_diceR_50d[,9],n_clust=3)


list_of_probs_50d <- list(hc_probs_50d,diana_probs_50d,km_probs_50d,pam_probs_50d,ap_probs_50d,sc_probs_50d,gmm_probs_50d,som_probs_50d,cmeans_probs_50d)

cBMA_output_50d <- clusterBMA::clusterBMA(input_data = simul_50d_df,cluster_prob_matrices = list_of_probs_50d,n_final_clust = 3,wt_crit_name = "Calinski_Harabasz",wt_crit_direction = "max")
cBMA_output_50d

cBMA_output_50d[[3]]
cBMA_output_50d[[5]]
```


# Combining outputs all into one DF

```{r}

true_labs_50d <- simul_50d_labels

plotting_df_50d <- data.frame(cbind(simul_50d_df,CSPA_output_50d,LCA_output_50d,LCE_output_50d,k_modes_output_50d,majority_voting_output_50d,cBMA_output_50d[[3]]$alloc_ordered,cBMA_output_50d[[3]]$alloc_prob,true_labs_50d))
# 
# names(plotting_df)
# length(plotting_df)
# plotting_df[,4:8] <- lapply(plotting_df[,4:8],as.factor)

names(plotting_df_50d)[ncol(plotting_df_50d)-2] <- "clusterBMA_output_50d" 
names(plotting_df_50d)[ncol(plotting_df_50d)-1] <- "clusterBMA_probs_50d" 

#view(plotting_df)
```


# comparing accuracy using Adjusted RAnd Index

```{r}
library(pdfCluster)

names(plotting_df_50d)


# CSPA
ARI_CSPA_50d <- pdfCluster::adj.rand.index(plotting_df_50d$CSPA_output_50d,plotting_df_50d$true_labs_50d)


# LCA
ARI_LCA_50d <- pdfCluster::adj.rand.index(plotting_df_50d$LCA_output_50d,plotting_df_50d$true_labs_50d)

# LCE
ARI_LCE_50d <- pdfCluster::adj.rand.index(plotting_df_50d$LCE_output_50d,plotting_df_50d$true_labs_50d)


# k_modes
ARI_k_modes_50d <- pdfCluster::adj.rand.index(plotting_df_50d$k_modes_output_50d,plotting_df_50d$true_labs_50d)


# majority_voting
ARI_majority_voting_50d <- pdfCluster::adj.rand.index(plotting_df_50d$majority_voting_output_50d,plotting_df_50d$true_labs_50d)


# clusterBMA
ARI_clusterBMA_50d <- pdfCluster::adj.rand.index(plotting_df_50d$clusterBMA_output_50d,plotting_df_50d$true_labs_50d)


highcertainty_threshold <- 0.8
ARI_clusterBMA_highcertainty_50d <- pdfCluster::adj.rand.index(plotting_df_50d$clusterBMA_output_50d[cBMA_output_50d[[3]]$alloc_prob>highcertainty_threshold],plotting_df_50d$true_labs_50d[cBMA_output_50d[[3]]$alloc_prob>highcertainty_threshold])

ARI_CSPA_50d
ARI_LCA_50d
ARI_LCE_50d
ARI_k_modes_50d
ARI_majority_voting_50d
ARI_clusterBMA_50d
ARI_clusterBMA_highcertainty_50d


# how many high-certainty (>90% alloc prob) allocations?

sum(cBMA_output_50d[[3]]$alloc_prob>highcertainty_threshold) #485/600


```


















#!!!!!!!!!!!!!!!!!!!!!



















# PIPELINE to generate 10 simulated datasets for each n. dimensions (2,10,50) and compare results from ensemble methods, saving ARI from each 10...

1. Generate 3 lists of 10 x simulated datasets
2. Write pipeline to apply all steps for each
3. Save ARI output from each iteration
4. generate summary stats for ARI


# NEED TO ADD: 5. save weights from cBMA (and other outputs? into list? probably helpful. list of lists...)

#### Leave out LCA as lacking citation and literature on application to ensemble clustering --> added based on GitHub request, citation/justification missing for application in an ensemble context #### 




1. Write pipeline to apply all steps for each
- cluster algs
- ensemble algs (mentioned in diceR paper)
- clusterBMA
- calculate and save ARI


```{r}


# COMPUTING CLUSTER ALGS


sim_pipeline_10sim_nd_function <- function(sim_data_list){
       
columns = c("ARI_CSPA","ARI_LCE","ARI_k_modes","ARI_majority_voting","ARI_clusterBMA","ARI_clusterBMA_highcertainty","proportion_highcertainty")
ARI_storage_df = data.frame(matrix(nrow = 1, ncol = length(columns))) 
colnames(ARI_storage_df) = columns


cBMA_results_store <- vector(mode="list")
        
for(i in 1:length(sim_data_list$datList)){
        
        simul_df <- sim_data_list$datList[[i]]
        
diceR_clusters <- diceR::consensus_cluster(data=simul_df,nk=3,p.item=1, algorithms = c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans"), reps = 1) #having issues with nmf and block bugs/performance- removing



# COMPUTING ENSEMBLE - CSPA, LCE, k-modes, majority voting (all 4 mentioned in diceR paper with cites for ensemble clustering application -- leaving out LCA as ambiguous literature basis/seems to be implemented based on GitHub request...)


CSPA_output <- CSPA(diceR_clusters,k=3)

LCE_output <- LCE(as.matrix(diceR_clusters[,1,,1]), k=3, sim.mat="cts")


k_modes_output <- k_modes(diceR_clusters, is.relabelled = F)

majority_voting_output <- majority_voting(diceR_clusters, is.relabelled = F)






#-------------------------------

# RUNNING CLUSTERBMA



cluster_labs_diceR <- as.matrix(diceR_clusters[,1,,1])

hc_probs <- hard_to_prob_fn(cluster_labs_diceR[,1],n_clust=3)
diana_probs <- hard_to_prob_fn(cluster_labs_diceR[,2],n_clust=3)
km_probs <- hard_to_prob_fn(cluster_labs_diceR[,3],n_clust=3)
pam_probs <- hard_to_prob_fn(cluster_labs_diceR[,4],n_clust=3)
ap_probs <- hard_to_prob_fn(cluster_labs_diceR[,5],n_clust=3)
sc_probs <- hard_to_prob_fn(cluster_labs_diceR[,6],n_clust=3)
gmm_probs <- hard_to_prob_fn(cluster_labs_diceR[,7],n_clust=3)
som_probs <- hard_to_prob_fn(cluster_labs_diceR[,8],n_clust=3)
cmeans_probs <- hard_to_prob_fn(cluster_labs_diceR[,9],n_clust=3)


list_of_probs <- list(hc_probs,diana_probs,km_probs,pam_probs,ap_probs,sc_probs,gmm_probs,som_probs,cmeans_probs)

cBMA_output <- clusterBMA::clusterBMA(input_data = simul_df,cluster_prob_matrices = list_of_probs,n_final_clust = 3,wt_crit_name = "Calinski_Harabasz",wt_crit_direction = "max")
cBMA_output
#cBMA_output_sdbw <- clusterBMA::clusterBMA(input_data = simul_df,cluster_prob_matrices = list_of_probs,n_final_clust = 3,wt_crit_name = "S_Dbw",wt_crit_direction = "min")



cBMA_output[[3]]
cBMA_output[[5]]

#cBMA_output_sdbw[[5]]
#cBMA_output[[5]]





#---------------------------

# COMBINING OUTPUTS INTO ONE DF






true_labs <- sim_data_list$memList[[i]]

plotting_df <- data.frame(cbind(simul_df,CSPA_output,LCE_output,k_modes_output,majority_voting_output,cBMA_output[[3]]$alloc_ordered,cBMA_output[[3]]$alloc_prob,true_labs))
# 
# names(plotting_df)
# length(plotting_df)
# plotting_df[,4:8] <- lapply(plotting_df[,4:8],as.factor)

names(plotting_df)[ncol(plotting_df)-2] <- "clusterBMA_output" 
names(plotting_df)[ncol(plotting_df)-1] <- "clusterBMA_probs" 

#view(plotting_df)



#------------------------------


# comparing accuracy using Adjusted RAnd Index


names(plotting_df)


# CSPA
ARI_CSPA <- pdfCluster::adj.rand.index(plotting_df$CSPA_output,plotting_df$true_labs)

# LCE
ARI_LCE <- pdfCluster::adj.rand.index(plotting_df$LCE_output,plotting_df$true_labs)


# k_modes
ARI_k_modes <- pdfCluster::adj.rand.index(plotting_df$k_modes_output,plotting_df$true_labs)


# majority_voting
ARI_majority_voting <- pdfCluster::adj.rand.index(plotting_df$majority_voting_output,plotting_df$true_labs)


# clusterBMA
ARI_clusterBMA <- pdfCluster::adj.rand.index(plotting_df$clusterBMA_output,plotting_df$true_labs)


highcertainty_threshold <- 0.8
ARI_clusterBMA_highcertainty <- pdfCluster::adj.rand.index(plotting_df$clusterBMA_output[cBMA_output[[3]]$alloc_prob>highcertainty_threshold],plotting_df$true_labs[cBMA_output[[3]]$alloc_prob>highcertainty_threshold])

ARI_CSPA
ARI_LCE
ARI_k_modes
ARI_majority_voting
ARI_clusterBMA
ARI_clusterBMA_highcertainty


# how many high-certainty (>90% alloc prob) allocations?

proportion_pts_in_highcertainty <- sum(cBMA_output[[3]]$alloc_prob>highcertainty_threshold) #569/600


ARI_vector <- c(ARI_CSPA,ARI_LCE,ARI_k_modes,ARI_majority_voting,ARI_clusterBMA,ARI_clusterBMA_highcertainty,proportion_pts_in_highcertainty)


ARI_storage_df <- rbind(ARI_storage_df,ARI_vector)

cBMA_results_store <- append(cBMA_results_store,cBMA_output)

print(paste("Completed loop", i, "in simulation pipeline for", deparse(substitute(sim_data_list))))
}


# remove leading row of NA's
ARI_storage_df <- ARI_storage_df[-1,]

return(list(ARI_storage_df,cBMA_results_store))

}



```



#2. Generate 3 lists of 10 x simulated datasets (x 3 levels of separation)... Running pipeline on 3 sep x 3 dim x 10 reps datasets

#quick demo
```{r}

# 
simdat_2d_quicktest <- clusterGeneration::genRandomClust(numClust=3,sepVal=0,numNonNoisy=2,numNoisy=0,clustSizes=c(rep(50,3)),numReplicate = 10,clustszind = 3)
# 
# 
# # test pipeline works with small dataset - 20 in each cluster, 2d
# test_pipeline_out <- sim_pipeline_10sim_nd_function(simdat_2d_quicktest)
#test_pipeline_out
#psych::describe(test_pipeline_out)
# seems good

```









# 3 clusters


```{r}

# Low separation -- sepVal = -0.15 compared to -.0.05



#2D lowsep
# 
# simdat_2d_10reps_500each_lowsep <- clusterGeneration::genRandomClust(numClust=3,sepVal=-0.15,numNonNoisy=2,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 10,clustszind = 3)
# 
# save(simdat_2d_10reps_500each_lowsep,file="sim_data_2d_10reps_500each_220123_lowsep")

load("sim_data_2d_10reps_500each_220123_lowsep")



#10D lowsep
# 
# simdat_10d_10reps_500each_lowsep <- clusterGeneration::genRandomClust(numClust=3,sepVal=-0.15,numNonNoisy=10,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 10,clustszind = 3)
# 
# save(simdat_10d_10reps_500each_lowsep,file="sim_data_10d_10reps_500each_220123_lowsep")

load("sim_data_10d_10reps_500each_220123_lowsep")


#50D lowsep
# 
# simdat_50d_10reps_500each_lowsep <- clusterGeneration::genRandomClust(numClust=3,sepVal=-0.15,numNonNoisy=50,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 10,clustszind = 3)
# 
# save(simdat_50d_10reps_500each_lowsep,file="sim_data_50d_10reps_500each_220123_lowsep")

load("sim_data_50d_10reps_500each_220123_lowsep")



#--------------


results_2d_10reps_500each_lowsep <- sim_pipeline_10sim_nd_function(simdat_2d_10reps_500each_lowsep)

results_10d_10reps_500each_lowsep <- sim_pipeline_10sim_nd_function(simdat_10d_10reps_500each_lowsep)

results_50d_10reps_500each_lowsep <- sim_pipeline_10sim_nd_function(simdat_50d_10reps_500each_lowsep)




# load("results_2d_10reps_500each_lowsep")
# load("results_10d_10reps_500each_lowsep")
# load("results_50d_10reps_500each_lowsep")
# 

ARI_table_2d_10reps_500each_lowsep <- results_2d_10reps_500each_lowsep[[1]]
cBMA_results_2d_10reps_500each_lowsep <- results_2d_10reps_500each_lowsep[[2]]


ARI_table_10d_10reps_500each_lowsep <- results_10d_10reps_500each_lowsep[[1]]
cBMA_results_10d_10reps_500each_lowsep <- results_10d_10reps_500each_lowsep[[2]]


ARI_table_50d_10reps_500each_lowsep <- results_50d_10reps_500each_lowsep[[1]]
cBMA_results_50d_10reps_500each_lowsep <- results_50d_10reps_500each_lowsep[[2]]


ARI_table_2d_10reps_500each_lowsep
psych::describe(ARI_table_2d_10reps_500each_lowsep)

ARI_table_10d_10reps_500each_lowsep
psych::describe(ARI_table_10d_10reps_500each_lowsep)

ARI_table_50d_10reps_500each_lowsep
psych::describe(ARI_table_50d_10reps_500each_lowsep)
# 
# 


# 
# save(results_2d_10reps_500each_lowsep,file="results_2d_10reps_500each_lowsep")
# save(results_10d_10reps_500each_lowsep,file="results_10d_10reps_500each_lowsep")
# save(results_50d_10reps_500each_lowsep,file="results_50d_10reps_500each_lowsep")

# 


```

```{r}

#-------------



# Medium separation sepVal = -0.05


#Medium separation
#2D
# 
# simdat_2d_10reps_500each_medsep <- clusterGeneration::genRandomClust(numClust=3,sepVal=-0.05,numNonNoisy=2,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 10,clustszind = 3)
# 
# save(simdat_2d_10reps_500each_medsep,file="sim_data_2d_10reps_500each_medsep_200123")

load("sim_data_2d_10reps_500each_medsep_200123")



#10D
# 
# simdat_10d_10reps_500each_medsep <- clusterGeneration::genRandomClust(numClust=3,sepVal=-0.05,numNonNoisy=10,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 10,clustszind = 3)
# 
# save(simdat_10d_10reps_500each_medsep,file="sim_data_10d_10reps_500each_medsep_200123")

load("sim_data_10d_10reps_500each_medsep_200123")


#50D

# simdat_50d_10reps_500each_medsep <- clusterGeneration::genRandomClust(numClust=3,sepVal=-0.05,numNonNoisy=50,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 10,clustszind = 3)
# 
# save(simdat_50d_10reps_500each_medsep,file="sim_data_50d_10reps_500each_medsep_200123")

load("sim_data_50d_10reps_500each_medsep_200123")


#-----



results_2d_10reps_500each_medsep <- sim_pipeline_10sim_nd_function(simdat_2d_10reps_500each_medsep)

results_10d_10reps_500each_medsep <- sim_pipeline_10sim_nd_function(simdat_10d_10reps_500each_medsep)

results_50d_10reps_500each_medsep <- sim_pipeline_10sim_nd_function(simdat_50d_10reps_500each_medsep)


ARI_table_2d_10reps_500each_medsep <- results_2d_10reps_500each_medsep[[1]]
cBMA_results_2d_10reps_500each_medsep <- results_2d_10reps_500each_medsep[[2]]


ARI_table_10d_10reps_500each_medsep <- results_10d_10reps_500each_medsep[[1]]
cBMA_results_10d_10reps_500each_medsep <- results_10d_10reps_500each_medsep[[2]]


ARI_table_50d_10reps_500each_medsep <- results_50d_10reps_500each_medsep[[1]]
cBMA_results_50d_10reps_500each_medsep <- results_50d_10reps_500each_medsep[[2]]


ARI_table_2d_10reps_500each_medsep
psych::describe(ARI_table_2d_10reps_500each_medsep)

ARI_table_10d_10reps_500each_medsep
psych::describe(ARI_table_10d_10reps_500each_medsep)

ARI_table_50d_10reps_500each_medsep
psych::describe(ARI_table_50d_10reps_500each_medsep)
# 
# 

# 
# 
# save(results_2d_10reps_500each_medsep,file="results_2d_10reps_500each_medsep")
# save(results_10d_10reps_500each_medsep,file="results_10d_10reps_500each_medsep")
# save(results_50d_10reps_500each_medsep,file="results_50d_10reps_500each_medsep")

# 
# load("results_2d_10reps_500each_medsep")
# load("results_10d_10reps_500each_medsep")
# load("results_50d_10reps_500each_medsep")

  
#-----------------------

# HIGH SEPARATION sepVal = 0.1




#2D highsep
# 
# simdat_2d_10reps_500each_highsep <- clusterGeneration::genRandomClust(numClust=3,sepVal=0.1,numNonNoisy=2,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 10,clustszind = 3)
# 
# save(simdat_2d_10reps_500each_highsep,file="sim_data_2d_10reps_500each_220123_highsep")

load("sim_data_2d_10reps_500each_220123_highsep")



#10D highsep

# simdat_10d_10reps_500each_highsep <- clusterGeneration::genRandomClust(numClust=3,sepVal=0.1,numNonNoisy=10,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 10,clustszind = 3)
# 
# save(simdat_10d_10reps_500each_highsep,file="sim_data_10d_10reps_500each_220123_highsep")

load("sim_data_10d_10reps_500each_220123_highsep")


#50D highsep
# 
# simdat_50d_10reps_500each_highsep <- clusterGeneration::genRandomClust(numClust=3,sepVal=0.1,numNonNoisy=50,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 10,clustszind = 3)
# 
# save(simdat_50d_10reps_500each_highsep,file="sim_data_50d_10reps_500each_220123_highsep")

load("sim_data_50d_10reps_500each_220123_highsep")



#--------------



results_2d_10reps_500each_highsep <- sim_pipeline_10sim_nd_function(simdat_2d_10reps_500each_highsep)

results_10d_10reps_500each_highsep <- sim_pipeline_10sim_nd_function(simdat_10d_10reps_500each_highsep)

results_50d_10reps_500each_highsep <- sim_pipeline_10sim_nd_function(simdat_50d_10reps_500each_highsep)


ARI_table_2d_10reps_500each_highsep <- results_2d_10reps_500each_highsep[[1]]
cBMA_results_2d_10reps_500each_highsep <- results_2d_10reps_500each_highsep[[2]]


ARI_table_10d_10reps_500each_highsep <- results_10d_10reps_500each_highsep[[1]]
cBMA_results_10d_10reps_500each_highsep <- results_10d_10reps_500each_highsep[[2]]


ARI_table_50d_10reps_500each_highsep <- results_50d_10reps_500each_highsep[[1]]
cBMA_results_50d_10reps_500each_highsep <- results_50d_10reps_500each_highsep[[2]]


ARI_table_2d_10reps_500each_highsep
psych::describe(ARI_table_2d_10reps_500each_highsep)

ARI_table_10d_10reps_500each_highsep
psych::describe(ARI_table_10d_10reps_500each_highsep)

ARI_table_50d_10reps_500each_highsep
psych::describe(ARI_table_50d_10reps_500each_highsep)
# 
# 

# 
# 
# save(results_2d_10reps_500each_highsep,file="results_2d_10reps_500each_highsep")
# save(results_10d_10reps_500each_highsep,file="results_10d_10reps_500each_highsep")
# save(results_50d_10reps_500each_highsep,file="results_50d_10reps_500each_highsep")

# 
# load("results_2d_10reps_500each_highsep")
# load("results_10d_10reps_500each_highsep")
# load("results_50d_10reps_500each_highsep")

```


# Plot showing example data for 2D simulations
```{r}

eg_sim_far <- clusterGeneration::genRandomClust(numClust=3,sepVal=0.1,numNonNoisy=2,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 1,clustszind = 3)
eg_sim_far_df <- eg_sim_far$datList$test_1

eg_sim_med <- clusterGeneration::genRandomClust(numClust=3,sepVal=-0.05,numNonNoisy=2,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 1,clustszind = 3)
eg_sim_med_df <- eg_sim_med$datList$test_1

eg_sim_close <- clusterGeneration::genRandomClust(numClust=3,sepVal=-0.15,numNonNoisy=2,numNoisy=0,clustSizes=c(rep(500,3)),numReplicate = 1,clustszind = 3)
eg_sim_close_df <- eg_sim_close$datList$test_1


far_eg_gg <- ggplot() + 
  geom_point(aes(x=eg_sim_far_df[,1],y=eg_sim_far_df[,2]))+ 
  xlab("")+ 
  ylab("")+
  guides(size = "none")+
  ggtitle("a) 2D Simulated data - High Separation") + theme_bw()



med_eg_gg <- ggplot() + 
  geom_point(aes(x=eg_sim_med_df[,1],y=eg_sim_med_df[,2]))+ 
  xlab("")+ 
  ylab("")+
  guides(size = "none")+
  ggtitle("b) 2D Simulated data - Medium Separation") + theme_bw()


close_eg_gg <- ggplot() + 
  geom_point(aes(x=eg_sim_close_df[,1],y=eg_sim_close_df[,2]))+ 
  xlab("")+ 
  ylab("")+
  guides(size = "none")+
  ggtitle("c) 2D Simulated data - Low Separation") + theme_bw()



png(file='sim_2d_eg_plots.png',width=1500,height=500,pointsize=22)
grid.arrange(far_eg_gg,med_eg_gg,close_eg_gg,nrow=1, ncol=3)
dev.off()


tiff("sim_2d_eg_plots.tif", compression = "lzw",width = 1500, height = 500, pointsize = 22)
grid.arrange(far_eg_gg,med_eg_gg,close_eg_gg,nrow=1, ncol=3)
dev.off()  

```



# Generate supplementary table for cBMA weights mean(sd) for sim study benchmark

```{r}

# HIGH SEPARATION

load("results_2d_10reps_500each_highsep")
load("results_10d_10reps_500each_highsep")
load("results_50d_10reps_500each_highsep")

#---

library(gtsummary)
weights_2d <- data.frame(matrix(ncol=9,nrow=0))

for(i in c(5,12,19,26,33,40,47,54,61,68)){
weights_2d <- rbind(weights_2d,results_2d_10reps_500each_highsep[[2]][[i]])
}

names(weights_2d) <- c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans")

#---


weights_10d <- data.frame(matrix(ncol=9,nrow=0))

for(i in c(5,12,19,26,33,40,47,54,61,68)){
weights_10d <- rbind(weights_10d,results_10d_10reps_500each_highsep[[2]][[i]])
}

names(weights_10d) <- c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans")


#---


weights_50d <- data.frame(matrix(ncol=9,nrow=0))

for(i in c(5,12,19,26,33,40,47,54,61,68)){
weights_50d <- rbind(weights_50d,results_50d_10reps_500each_highsep[[2]][[i]])
}

names(weights_50d) <- c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans")


#-----------

# Formatted tables

weights_2d_gt <- weights_2d   %>% 
    tbl_summary(
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = everything() ~ 3,
      missing="no"
    ) %>% 
     modify_header(label = "2D Simulated Data")
  # gtsummary::as_gt() %>%
  # gt::as_latex()



weights_10d_gt <- weights_10d   %>% 
    tbl_summary(
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = everything() ~ 3,
      missing="no"
    ) %>% 
     modify_header(label = "10D Simulated Data")
  # gtsummary::as_gt() %>%
  # gt::as_latex()



weights_50d_gt <- weights_50d   %>% 
    tbl_summary(
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = everything() ~ 3,
      missing="no"
    ) %>% 
     modify_header(label = "50D Simulated Data")
  # gtsummary::as_gt() %>%
  # gt::as_latex()


# Combine them
combined_weights_tbl <- tbl_merge(list(weights_2d_gt,weights_10d_gt,weights_50d_gt),tab_spanner = F)


combined_weights_tbl %>% 
  gtsummary::as_gt() %>%
  gt::as_raw_html()
```


```{r}
# MEDIUM SEPARATION


load("results_2d_10reps_500each_medsep")
load("results_10d_10reps_500each_medsep")
load("results_50d_10reps_500each_medsep")

#---

library(gtsummary)
weights_2d <- data.frame(matrix(ncol=9,nrow=0))

for(i in c(5,12,19,26,33,40,47,54,61,68)){
weights_2d <- rbind(weights_2d,results_2d_10reps_500each_medsep[[2]][[i]])
}

names(weights_2d) <- c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans")

#---


weights_10d <- data.frame(matrix(ncol=9,nrow=0))

for(i in c(5,12,19,26,33,40,47,54,61,68)){
weights_10d <- rbind(weights_10d,results_10d_10reps_500each_medsep[[2]][[i]])
}

names(weights_10d) <- c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans")


#---


weights_50d <- data.frame(matrix(ncol=9,nrow=0))

for(i in c(5,12,19,26,33,40,47,54,61,68)){
weights_50d <- rbind(weights_50d,results_50d_10reps_500each_medsep[[2]][[i]])
}

names(weights_50d) <- c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans")


#-----------

# Formatted tables

weights_2d_gt <- weights_2d   %>% 
    tbl_summary(
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = everything() ~ 3,
      missing="no"
    ) %>% 
     modify_header(label = "2D Simulated Data")
  # gtsummary::as_gt() %>%
  # gt::as_latex()



weights_10d_gt <- weights_10d   %>% 
    tbl_summary(
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = everything() ~ 3,
      missing="no"
    ) %>% 
     modify_header(label = "10D Simulated Data")
  # gtsummary::as_gt() %>%
  # gt::as_latex()



weights_50d_gt <- weights_50d   %>% 
    tbl_summary(
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = everything() ~ 3,
      missing="no"
    ) %>% 
     modify_header(label = "50D Simulated Data")
  # gtsummary::as_gt() %>%
  # gt::as_latex()


# Combine them
combined_weights_tbl <- tbl_merge(list(weights_2d_gt,weights_10d_gt,weights_50d_gt),tab_spanner = F)


combined_weights_tbl %>% 
  gtsummary::as_gt() %>%
  gt::as_raw_html()
```

```{r}
# LOW SEPARATION


load("results_2d_10reps_500each_lowsep")
load("results_10d_10reps_500each_lowsep")
load("results_50d_10reps_500each_lowsep")

#---

library(gtsummary)
weights_2d <- data.frame(matrix(ncol=9,nrow=0))

for(i in c(5,12,19,26,33,40,47,54,61,68)){
weights_2d <- rbind(weights_2d,results_2d_10reps_500each_lowsep[[2]][[i]])
}

names(weights_2d) <- c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans")

#---


weights_10d <- data.frame(matrix(ncol=9,nrow=0))

for(i in c(5,12,19,26,33,40,47,54,61,68)){
weights_10d <- rbind(weights_10d,results_10d_10reps_500each_lowsep[[2]][[i]])
}

names(weights_10d) <- c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans")


#---


weights_50d <- data.frame(matrix(ncol=9,nrow=0))

for(i in c(5,12,19,26,33,40,47,54,61,68)){
weights_50d <- rbind(weights_50d,results_50d_10reps_500each_lowsep[[2]][[i]])
}

names(weights_50d) <- c("hc", "diana", "km", "pam", "ap", "sc",
"gmm", "som", "cmeans")


#-----------

# Formatted tables

weights_2d_gt <- weights_2d   %>% 
    tbl_summary(
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = everything() ~ 3,
      missing="no"
    ) %>% 
     modify_header(label = "2D Simulated Data")
  # gtsummary::as_gt() %>%
  # gt::as_latex()



weights_10d_gt <- weights_10d   %>% 
    tbl_summary(
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = everything() ~ 3,
      missing="no"
    ) %>% 
     modify_header(label = "10D Simulated Data")
  # gtsummary::as_gt() %>%
  # gt::as_latex()



weights_50d_gt <- weights_50d   %>% 
    tbl_summary(
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    digits = everything() ~ 3,
      missing="no"
    ) %>% 
     modify_header(label = "50D Simulated Data")
  # gtsummary::as_gt() %>%
  # gt::as_latex()


# Combine them
combined_weights_tbl <- tbl_merge(list(weights_2d_gt,weights_10d_gt,weights_50d_gt),tab_spanner = F)


combined_weights_tbl %>% 
  gtsummary::as_gt() %>%
  gt::as_raw_html()
```








